---
title: "project 8"
author: "George Pitsavas"
date: "12/8/2020"
output: html_document
---

# Data Preparation
```{r}

library(caret)
library(rpart)
library(randomForest)
library(gbm)
library(e1071)
set.seed(1234)
```
# Downloading data

# For training data
```{r}
trainingDataUrl<-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
trainingData<-read.csv(url(trainingDataUrl),na.strings = c("NA","#DIV/0!",""))
```

# For test data
```{r}
testingDataUrl<- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testingData<-read.csv(url(testingDataUrl),na.strings = c("NA","#DIV/0!",""))
```

```{r}
dim(trainingData)
dim(testingData)
```
Removing missing values from training data.

```{r}
sum(is.na(trainingData))
trainingData<-trainingData[,colSums(is.na(trainingData))==0]
trainingData<-trainingData[,-c(1:7)]

dim(trainingData)
```

Removing missing values from test data

```{r}
is.na(testingData)
testingData<-testingData[,colSums(is.na(testingData))==0]
testingData<-testingData[,-c(1:7)]

dim(testingData)
```


# Partitioning in training dataset
```{r}
NEWdata<-createDataPartition(trainingData$classe,p=0.7,list=F)
trainingNEWdata<-trainingData[NEWdata,]
testingNEWdata<-trainingData[-NEWdata,]

dim(trainingNEWdata)
dim(testingNEWdata)
```

```{r}
ggplot(data = trainingNEWdata,aes(classe))+geom_bar(fill="darkslateblue")+labs(title = "Frequency of Different Levels",y="Frequency")
```
According to the plot about frequency distribution, it reveals that level A is most frequent and level D is the least one in training dataset.


# Prediction using Random Forest

```{r}
summary(testingNEWdata)
modelRF<- randomForest(as.factor(classe) ~., data = trainingNEWdata, method="class")
predictionRF<- predict(modelRF, testingNEWdata, type= "class")
confusionMatrix(table(predictionRF,testingNEWdata$classe))
```
The accurancy of the random forest model is 99,51%

# Prediction using Generalized Boosted Model
```{r}
fitcontrol<-trainControl(method = "repeatedcv",number = 5,repeats = 1)
modelGBM<-train(classe~.,data=trainingNEWdata,method="gbm",trControl=fitcontrol,verbose=F)

predictionGBM<-predict(modelGBM,testingNEWdata)
confusionMatrix(table(predictionGBM,testingNEWdata$classe))
```
The accurancy of the Generalized Boosted Model is 96,69%. It is obviously smaller value than random forest's accuracy.Thus we gonna use the prediction that are made via random Forest method , because it is more accurate.We will apply to random forest model the prediction we need for the 20 quiz results.



```{r}
predictTest<- predict(modelRF,testingData)
predictTest
```
